Flowchart of Current Algorithm

### 2008-10-12 docs/flowchart/paper.tex
add more MarginPars pointing out where updating is needed

\section{Current Algorithm}
\subsection{Notation}

@@

\item For any quantity, $\phi,$ we define $\overline{\phi} = ${\bf Avg}$(\phi),$ 
the average over $\Omega_H,$ as
\begin{equation}
\overline{\phi}(r) = \frac{1}{\mathrm{A}(\Omega_H)}\int_{\Omega_H} \phi(r,{\bf x}) \; dA \enskip .
\end{equation}

\item {\bf React State}$[\rho^{\inp},(\rho h)^{\inp},X_k^{\inp},T^{\inp}, (\rho\Hext)^{\inp}]\rightarrow$
$[\rho^{\outp}, (\rho h)^{\outp}, X_k^{\outp}, T^{\outp}, (\rho \omegadot_k)^{\outp}]$ \newline
is the process by which we evolve the species and enthalpy from $X_k^{\inp} \rightarrow X_k^{\outp}$ 
and $(\rho h)^{\inp} \rightarrow (\rho h)^{\outp}$ by solving the following system of equations 
over a time interval of  $\Delta t/2$,
\begin{eqnarray}
\frac{\partial X_k}{\partial t} &=& \omegadot_k\enskip,\\
\frac{\partial (\rho h)}{\partial t} &=& \rho \Hnuc + \rho \Hext\enskip .
\end{eqnarray}
  In particular, to evolve the species, we solve the system:
\begin{eqnarray}
\frac{dX_k}{dt} &=& \omegadot_k(\rho,X_k,T)\enskip, \\
\frac{dT}{dt} &=&\frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right )\enskip. \label{eq:reacttemp}
\end{eqnarray}
using the stiff ordinary differential equation integration methods
provided by the {\tt VODE} package (cite VODE).  The absolute error
tolerances are set to $10^{-12}$ for the species, and a relative
tolerance of $10^{-5}$ is used for the temperature.  The integration
yields the new values of the mass fractions, $X_k^{\outp}$.  Equation
(\ref{eq:reacttemp}) is derived from the full temperature evolution equation
\begin{equation}
\label{eq:tempenthalpy}
\frac{DT}{Dt} = \frac{1}{\rho c_p} \left[ \left(1 - \rho h_p\right) \frac{D p}{D t}
 - \sum_k \rho \xi_k {\omegadot}_k 
 + \rho \Hnuc + \rho \Hext \right] \enskip , 
\end{equation}
(paper III; eq.~[8])
by assuming that the pressure is constant during the burn state.  In
evolving these equations, we need to evaluate $c_p$ and $\xi_k$.  In
theory, this means evaluating the equation of state for each
right-hand side evaluation that {\tt VODE} requires.  In practice, we
freeze $c_p$ and $\xi_k$ at the start of the integration time step and
compute them using $\rho^{\inp}, X_k^{\inp},$ and $T^{\inp}$ as inputs
to the equation of state.  We note that while temperature is evolved
when solving these equations, we do not keep the final temperature,
nor do we use it to compute the final change in enthalpy.  Therefore,
$T^{\outp} = T^{\inp}$.  Also, note that the density remains unchanged
during the {\bf React State} step, i.e., $\rho^{\outp} = \rho^{\inp}$.

After the new mass fractions have been computed, the reaction rates are defined as:
\begin{equation}
(\rho\omegadot_k)^{\outp} = \frac{\rho^{\outp} ( X_k^{\outp} - X_k^{\inp})}{\Delta t /2} \enskip,
\end{equation}
and the nuclear energy generation rate is defined as
\begin{equation}
(\rho\Hnuc) = -\sum_k(\rho\omegadot_k)^{\outp} \; q_k \enskip.
\end{equation}
The enthalpy update incorporates the external heating, $(\rho\Hext)^{\inp}$, and is updated by
\begin{equation}
(\rho h)^{\outp} = (\rho h)^{\inp} + \frac{\dt}{2} (\rho\Hnuc) + \frac{\dt}{2} (\rho\Hext)^{\inp}\enskip.
\end{equation}

\item {\bf Advect Base}$(\rho_0^{\inp}, p_0^{\inp}, \beta_0^{\inp}, w_0^{\inp}, \psi^{\inp} ) \rightarrow 
(\rho_0^{\outp}, \rho_0^{\outp,n+\myhalf}, p_0^{\outp})$ 
\newline
is the process by which we update the base state through $\dt$ in time \MarginPar{we need a separate section for spherical}
given the radial velocity $w_0^{\inp}.$ Here we discuss the algorithm
for plane-parallel geometries.  The base state arrays are all
one-dimensional in the radial coordinate; we think of the base state
quantities as defined at cell centers, with $w_0$ and $\beta_0$
defined halfway in-between.\\ \\ a) For the density update, we
discretize equation the base state density evolution equation
\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
- \nablab \cdotb \left( \etarho \er \right) \enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}
(paper III; eq.~[29]), neglecting the $\etarho$ term, to compute the
new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ] \nonumber  \enskip,
\end{eqnarray}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the
procedure described in paper II, Appendix A, and are saved for use
later in the overall algorithm.\\ \\ b) For the pressure update, we
discretize the base state pressure evolution equation,
\begin{equation}
\frac{\partial p_0}{\partial t} = w_0 \rho_0 g  + \etarho g
                                 = - w_0 \frac{\partial p_0}{\partial r} + \etarho g \enskip .
\label{eq:p0upd_new}
\end{equation}
(paper III; eq.~[31]) to compute the new base state pressure,
\begin{eqnarray}
p_{0,j}^\outp &=& p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\inp \enskip,
\end{eqnarray}
where the interface states are again found via the procedure described in
paper II, Appendix A.\\ \\
c)  For the enthalpy update, \MarginPar{We need enthalpy equations now that we are predicting $(\rho h)'$.}
\\

\item {\bf Correct Base}$(\rho_0^{\inp} , \etarho^{\inp}) \rightarrow (\rho_0^{\outp})$
is the process by which we adjust the base state density given $\etarho$ using
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left( \eta_{\rho,j+\myhalf}^{\inp} - \eta_{\rho,j-\myhalf}^{\inp}  \right)  \enskip . 
\end{eqnarray} 
\end{enumerate}

@@

\item Construct $w_0^{\nph,\star}$ by integrating
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g \enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh},$ \MarginPar{note: this is true only for plane-parallel}
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}} \psi^{\nmh} \enskip . \nonumber
\end{equation}
For spherical geometries, this equation would be modified.

@@

\item {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho^n \Hext)]
                   \rightarrow$ $[ \rho^{(1)}, (\rho h)^{(1)}, X_k^{(1)}, T^{(1)},
                                  (\rho \omegadot_k)^{(1)} ].$

@@

\item Define an edge-centered $\etarho^{\nph,\star}$ and cell-centered $\psi_j^{\nph,\star}$:
\begin{eqnarray}
 \etarho^{\nph,\star}   &=&  {\rm {\bf Avg}} \left( (\uadvone \cdotb \er + w_0^{\nph,\star}) 
\rho^{(1),\nph,\star} \right) - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} 
 \nonumber \enskip , \\
 \psi_j^{\nph,\star}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{eqnarray}
For spherical geometries, $\psi_j^{\nph,\star}$ would have a different form.

@@

\item {\bf React State}$( \rho^{(2),\star},(\rho h)^{(2),\star}, X_k^{(2),\star}, 
                             T^{(2),\star}, (\rho^{(2),\star} \Hext)) $\\
$\rightarrow ( \rho^{n+1,\star},(\rho h)^{n+1,\star}, X_k^{n+1,\star}, T^{n+1,\star}, 
              (\rho \omegadot_k)^{(2),\star} ).$

@@

\item Construct $w_0^{\nph}$ by integrating equation (\ref{eq:divw0}),
\MarginPar{this is plane-parallel only}
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} =  \overline{S}^{\nph,\star} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}} \psi^{\nph,\star} \enskip , \nonumber
\end{equation}
for plane-parallel geometries, where 
$\gammabar^{\nph,\star} = (\gammabar^{n} + \gammabar^{n+1,\star} ) / 2 $ and
$ p_0^{\nph,\star} = (p_0^{n} + p_0^{n+1,\star} ) / 2.$

@@

\item Compute the edge states, $(\rho X_k)^{(1),\nph}$ and $(\rho h)^{(1),\nph},$
      for the conservative update of $(\rho X_k)$ and $(\rho h).$  Here we
      predict $\rho'$, $(\rho h)'$, and $X_k$ to the edges, using
      a second-order Taylor expansion in space and time, as described in
      paper II, Appendix A, using $\V = \uadvtwo+w_0^{\nph} \er$. 
      Again, we do not include the reaction terms in the enthalpy prediction 
      since we accounted for them already in {\bf React State}.
      We use the base state density, $\rho_0$, and base state enthalpy, $(\rho h)_0$,
      to convert these to edge states for $(\rho X_k)$ and $(\rho h)$. 
      We define $\rho^{(1),\nph} = \sum_k (\rho X_k)^{(1),\nph}.$

@@

\item Define an edge-centered $ \etarho^{\nph}$ and a cell-centered $\psi_j^{\nph}$,
\begin{eqnarray}
 \etarho^{\nph}   &=&  {\rm {\bf Avg}} \left( (\uadvtwo \cdotb \er + w_0^{\nph}) 
\rho^{(1),\nph} \right) - w_0^{\nph} \rho_0^{\nph,{\rm pred}} 
 \nonumber \enskip , \\
 \psi_j^{\nph}  &=&  \frac{1}{2} \left(\eta_{rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{eqnarray}

@@

\item {\bf React State}$(\rho^{(2)},(\rho h)^{(2)}, X_k^{(2)},T^{(2)}, (\rho^{(2)} \Hext) )
                   \rightarrow (\rho^{n+1}, (\rho h)^{n+1}, X_k^{n+1}, T^{n+1}, 
                               (\rho \omegadot_k)^{(2)} ).$

>>>>

\section{Current Algorithm}

Here we outline the algorithm currently implemented in the code.  Our
starting point for this description are the series of papers describing
the development of the algorithm:
\begin{itemize}
\item {\em Low Mach Number Modeling of Type Ia
  Supernovae. I. Hydrodynamics}, A.~S.~Almgren, J.~B.~Bell, 
  C.~A.~Rendleman, \& M.~Zingale 2006, ApJ, 637, 922 (henceforth
  paper~I)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. II. Energy
  Evolution} A.~S.~Almgren, J.~B.~Bell, C.~A.~Rendleman, \& M.~Zingale
  2006, ApJ, 649, 927 (henceforth paper~II)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. III. Reactions}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale
  2008, ApJ, 684, 449 (henceforth paper~III)
\end{itemize}

\subsection{Notation}

@@

\item For any quantity, $\phi,$ we define $\overline{\phi} = ${\bf Avg}$(\phi),$ 
the average over $\Omega_H,$ as
\begin{equation}
\overline{\phi}(r) = \frac{1}{\mathrm{A}(\Omega_H)}\int_{\Omega_H} \phi(r,{\bf x}) \; dA \enskip .
\end{equation}
here $\Omega_H$ is a layer at constant radius $r$. \MarginPar{we should discuss the implementation of average for spherical here}

\item {\bf React State}$[\rho^{\inp},(\rho h)^{\inp},X_k^{\inp},T^{\inp}, (\rho\Hext)^{\inp}]\rightarrow$
$[\rho^{\outp}, (\rho h)^{\outp}, X_k^{\outp}, T^{\outp}, (\rho \omegadot_k)^{\outp}, (\rho\Hnuc)^{\outp}]$ \newline
is the process by which we evolve the species and enthalpy from $X_k^{\inp} \rightarrow X_k^{\outp}$ 
and $(\rho h)^{\inp} \rightarrow (\rho h)^{\outp}$ by solving the following system of equations 
over a time interval of  $\Delta t/2$,
\begin{eqnarray}
\frac{\partial X_k}{\partial t} &=& \omegadot_k\enskip,\\
\frac{\partial (\rho h)}{\partial t} &=& \rho \Hnuc + \rho \Hext\enskip .
\end{eqnarray}
  In particular, to evolve the species, we solve the system:
\begin{eqnarray}
\frac{dX_k}{dt} &=& \omegadot_k(\rho,X_k,T)\enskip, \\
\frac{dT}{dt} &=&\frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right )\enskip. \label{eq:reacttemp}
\end{eqnarray}
using the stiff ordinary differential equation integration methods
provided by the {\tt VODE} package (cite VODE).  The absolute error
tolerances are set to $10^{-12}$ for the species, and a relative
tolerance of $10^{-5}$ is used for the temperature.  The integration
yields the new values of the mass fractions, $X_k^{\outp}$.  Equation
(\ref{eq:reacttemp}) is derived from the full temperature evolution equation
\begin{equation}
\label{eq:tempenthalpy}
\frac{DT}{Dt} = \frac{1}{\rho c_p} \left[ \left(1 - \rho h_p\right) \frac{D p}{D t}
 - \sum_k \rho \xi_k {\omegadot}_k 
 + \rho \Hnuc + \rho \Hext \right] \enskip , 
\end{equation}
(paper III; eq.~[8])
by assuming that the pressure is constant during the burn state.  In
evolving these equations, we need to evaluate $c_p$ and $\xi_k$.  In
theory, this means evaluating the equation of state for each
right-hand side evaluation that {\tt VODE} requires.  In practice, we
freeze $c_p$ and $\xi_k$ at the start of the integration time step and
compute them using $\rho^{\inp}, X_k^{\inp},$ and $T^{\inp}$ as inputs
to the equation of state.  We note that while temperature is evolved
when solving these equations, we do not keep the final temperature,
nor do we use it to compute the final change in enthalpy.  Therefore,
$T^{\outp} = T^{\inp}$.  Also, note that the density remains unchanged
during the {\bf React State} step, i.e., $\rho^{\outp} = \rho^{\inp}$.

After the new mass fractions have been computed, the reaction rates are defined as:
\begin{equation}
(\rho\omegadot_k)^{\outp} = \frac{\rho^{\outp} ( X_k^{\outp} - X_k^{\inp})}{\Delta t /2} \enskip,
\end{equation}
and the nuclear energy generation rate is defined as
\begin{equation}
(\rho\Hnuc) = -\sum_k(\rho\omegadot_k)^{\outp} \; q_k \enskip.
\end{equation}
for the case where only strong-mediated reactions are involved.  As
$\Hnuc$ is an output of the reaction network, more general networks
(i.e.\ involving weak interactions) can easily be added.  The enthalpy
update incorporates the external heating, $(\rho\Hext)^{\inp}$, and is
updated by
\begin{equation}
(\rho h)^{\outp} = (\rho h)^{\inp} + \frac{\dt}{2} (\rho\Hnuc) + \frac{\dt}{2} (\rho\Hext)^{\inp}\enskip.
\end{equation}

\item {\bf Advect Base}$(\rho_0^{\inp}, p_0^{\inp}, \beta_0^{\inp}, w_0^{\inp}, \psi^{\inp} ) \rightarrow 
(\rho_0^{\outp}, \rho_0^{\outp,n+\myhalf}, p_0^{\outp})$ 
\newline
is the process by which we update the base state through $\dt$ in
time \MarginPar{we need a separate section for spherical} given the
radial velocity $w_0^{\inp}.$ The base state arrays are all
one-dimensional in the radial coordinate; we think of the base state
quantities as defined at cell centers, with $w_0$ and $\beta_0$
defined halfway in-between.

\begin{enumerate}
\renewcommand{\theenumii}{{\bf \alph{enumii}}}

\item plane-parallel

\begin{enumerate}
\item For the density update, we discretize equation the base state
  density evolution equation
\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
- \nablab \cdotb \left( \etarho \er \right) \enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}
(paper III; eq.~[29]), neglecting the $\etarho$ term, to compute the
new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ] \nonumber  \enskip,
\end{eqnarray}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the
procedure described in paper II, Appendix A, and are saved for use
later in the overall algorithm.

\item For the pressure update, we discretize the base state pressure
  evolution equation,
\begin{equation}
\frac{\partial p_0}{\partial t} = w_0 \rho_0 g  + \etarho g
                                 = - w_0 \frac{\partial p_0}{\partial r} + \etarho g \enskip .
\label{eq:p0upd_new}
\end{equation}
(paper III; eq.~[31]) to compute the new base state pressure,
\begin{eqnarray}
p_{0,j}^\outp &=& p_{0,j}^\inp - \frac{\dt}{2\dr} \left (w_{0,j+\myhalf}^\inp
+ w_{0,j-\myhalf}^\inp \right)
\left (p_{0,j+\myhalf}^{n+\myhalf} -p_{0,j-\myhalf}^{n+\myhalf} \right ) + \dt \; \psi_j^\inp \enskip,
\end{eqnarray}
where the interface states are again found via the procedure described
in paper II, Appendix A.

\item For the enthalpy update, \MarginPar{We need enthalpy equations
  now that we are predicting $(\rho h)'$.}  
\end{enumerate}

\item spherical

\MarginPar{we need to write the spherical description}

\item {\bf Correct Base}$(\rho_0^{\inp} , \etarho^{\inp}) \rightarrow (\rho_0^{\outp})$
is the process by which we adjust the base state density given $\etarho$ using
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left( \eta_{\rho,j+\myhalf}^{\inp} - \eta_{\rho,j-\myhalf}^{\inp}  \right)  \enskip . 
\end{eqnarray} 
\end{enumerate}
\MarginPar{need to add spherical}

@@

\item Construct $w_0^{\nph,\star}$ by integrating

\begin{enumerate}
\renewcommand{\labelenumii}{\roman{enumii}.}
\item plane-parallel
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g \enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh},$ \MarginPar{note: this is true only for plane-parallel}
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}} \psi^{\nmh} \enskip . \nonumber
\end{equation}

\item spherical

\MarginPar{need to add spherical}
\end{enumerate}

@@

\item {\bf React State}$[\rho^n, (\rho h)^n, X_k^n, T^n, (\rho^n \Hext)]
                   \rightarrow$ $[ \rho^{(1)}, (\rho h)^{(1)}, X_k^{(1)}, T^{(1)},
                                  (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)} ].$

@@

\item Define an edge-centered $\etarho^{\nph,\star}$ and cell-centered $\psi_j^{\nph,\star}$:

\begin{enumerate}
\renewcommand{\labelenumii}{\roman{enumii}.}

\item plane-parallel

\begin{eqnarray}
 \etarho^{\nph,\star}   &=&  {\rm {\bf Avg}} \left( (\uadvone \cdotb \er + w_0^{\nph,\star}) 
\rho^{(1),\nph,\star} \right) - w_0^{\nph,\star} \rho_0^{\nph,\star,{\rm pred}} 
 \nonumber \enskip , \\
 \psi_j^{\nph,\star}  &=&  \frac{1}{2} \left(\eta_{\rho,j-\myhalf}^{\nph,\star} + \eta_{\rho,j+\myhalf}^{\nph,\star}\right) g \enskip .
\end{eqnarray}

\item spherical

\MarginPar{need to add spherical here}
\end{enumerate}

@@

\item {\bf React State}$( \rho^{(2),\star},(\rho h)^{(2),\star}, X_k^{(2),\star}, 
                             T^{(2),\star}, (\rho^{(2),\star} \Hext)) $\\
$\rightarrow ( \rho^{n+1,\star},(\rho h)^{n+1,\star}, X_k^{n+1,\star}, T^{n+1,\star}, 
              (\rho \omegadot_k)^{(2),\star}, (\rho \Hnuc)^{(2),\star} ).$

@@

\item Construct $w_0^{\nph}$ by integrating equation (\ref{eq:divw0}),

\begin{enumerate}
\renewcommand{\labelenumii}{\roman{enumii}.}

\item plane-parallel

\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} =  \overline{S}^{\nph,\star} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}} \psi^{\nph,\star} \enskip , \nonumber
\end{equation}
for plane-parallel geometries, where 
$\gammabar^{\nph,\star} = (\gammabar^{n} + \gammabar^{n+1,\star} ) / 2 $ and
$ p_0^{\nph,\star} = (p_0^{n} + p_0^{n+1,\star} ) / 2.$

\item spherical

\MarginPar{need to discuss spherical}

@@

\item Compute the edge states, $(\rho X_k)^{(1),\nph}$ and $(\rho h)^{(1),\nph},$
      for the conservative update of $(\rho X_k)$ and $(\rho h).$  Here we
      predict $\rho'$, $(\rho h)'$, and $X_k$ to the edges, using
      a second-order Taylor expansion in space and time, as described in
      paper II, Appendix A, using $\V = \uadvtwo+w_0^{\nph} \er$. 
      Again, we do not include the reaction terms in the enthalpy prediction 
      since we accounted for them already in {\bf React State}.
      We use the base state density, $\rho_0$, and base state enthalpy, $(\rho h)_0$,
      to convert these to edge states for $(\rho X_k)$ and $(\rho h)$. 
      We define $\rho^{(1),\nph} = \sum_k (\rho X_k)^{(1),\nph}.$ \MarginPar{we split this into two now}

@@

\item Define an edge-centered $ \etarho^{\nph}$ and a cell-centered $\psi_j^{\nph}$,

\begin{enumerate}
\renewcommand{\labelenumii}{\roman{enumii}.}

\item plane-parallel

\begin{eqnarray}
 \etarho^{\nph}   &=&  {\rm {\bf Avg}} \left( (\uadvtwo \cdotb \er + w_0^{\nph}) 
\rho^{(1),\nph} \right) - w_0^{\nph} \rho_0^{\nph,{\rm pred}} 
 \nonumber \enskip , \\
 \psi_j^{\nph}  &=&  \frac{1}{2} \left(\eta_{rho,j-\myhalf}^{\nph} + \eta_{\rho,j+\myhalf}^{\nph}\right) g \enskip .
\end{eqnarray}

\item spherical

@@

\item {\bf React State}$(\rho^{(2)},(\rho h)^{(2)}, X_k^{(2)},T^{(2)}, (\rho^{(2)} \Hext) )
                   \rightarrow (\rho^{n+1}, (\rho h)^{n+1}, X_k^{n+1}, T^{n+1}, 
                               (\rho \omegadot_k)^{(2)}, (\rho \Hnuc)^{(2)} ).$
